% Proposal Main Body %
% Author: Konstantinos Garas
% E-mail: kgaras041@gmail.com // k.gkaras@student.rug.nl
% Created: Sun 12 Oct 2025 @ 19:10:54 +0200
% Modified: Tue 04 Nov 2025 @ 23:01:24 +0100

\section*{Description}
This internship project with \href{https://innatera.com/}{Innatera Nanosystems} will see me take the role of a data engineer and data scientist. The overarching goal of the project is to help the company build a proper dataset so that they can sufficiently train their Machine Learning models.

The company focuses on using micro-controllers alongside neuromorphic neural-networks to build pattern recognition schemes that are power efficient and fast. My role in this internship will be on the practical aspect of things. More specifically, I will work with sensors and collect data valuable for the training of these neural-networks, and also statistically analyse the datasets produced to spot irregularities and anomalies.

The latest update that I have is that the project will last approximately 6 months. It has been asked of me to start on Monday November 24th, and so the end-date would be somewhere in the end of April. This information is clarified excessively in the official Internship Agreement Form.

\section*{Timetable}
The Lead Engineer of the team, as well as the Human Resources team has asked me to officially start the internship at \textbf{November 24th}. Calculating ahead 6 months, the project should end sometime at the end of \textbf{April 2026}, however, I don't have direct confirmation of this. 
